A Quantitative Genetic Linked Selection Model of the Negative Selection Process in Humans

### 2023-07-10 manuscript/manuscript.tex
fig checking

\begin{abstract} 
% TODO: emphasize connection to nearly neutral theory

@@

\section*{Results: Confirmation of Theory}

@@

Our predictions are qualitatively consistent with the observed divergence along
the human lineage (Figure \ref{fig:figure-6}). As expected, the predicted
substitution rate in features unlikely to be under selective constraint is very
close to the mutation rate. Throughout, we report our substitution rates as a
percent relative to the total mutation rate, $\mu$ (here fixed to $1.5 \times
10^{-8}$). In our PhastCons Priority model, introns and UTRs are estimated to
have have substitution rates that are $93.6\%$ of the mutation rate, and the
``other" feature is estimated at $97.8\%$. When we use the constrained grid,
these change to $97.85\%$ and $99.98\%$ respectively. By contrast, our
predicted substitution rates for PhastCons regions are much lower: $0.48\%$ for
the default grid, and $1.65\%$ for the constrained grid. This is likely due to
the constrained grid placing more of the DFE mass on weaker selection
coefficients, which in turn have a higher chance of drifting up to fixation.

@@

>>>>

\begin{abstract}

    Previous work has shown that negative selection against the steady influx
    of deleterious mutations is the predominant process shaping genome-wide
    patterns of genetic diversity in humans. This process leaves a ``linked
    selection signal"

    The classic population genetic
    model of this process, background selection, considers

    % TODO: emphasize connection to nearly neutral theory

@@

\section*{Results: Validation of Theory}

@@

Our predictions are qualitatively consistent with the observed divergence along
the human lineage (Figure \ref{fig:figure-6}). As expected, the predicted
substitution rate in features unlikely to be under selective constraint is very
close to the mutation rate. Throughout, we report our substitution rates as a
percent relative to the total mutation rate, $\mu$ (here fixed to $1.5 \times
10^{-8}$). In our PhastCons Priority model, introns and UTRs are estimated to
have have substitution rates that are $93.6\%$ of the mutation rate, and the
``other" feature is estimated at $97.8\%$.  When we use the constrained grid,
these change to $97.85\%$ and $99.98\%$ respectively. In our PhyloFit
estimates, the divergence rate in introns is $92.44\%$, 5' UTRs $75.5\%$, and
3' UTRs $72.65\%$. By contrast, our predicted substitution rates for PhastCons
regions are much lower: $0.48\%$ for the default grid, and $1.65\%$ for the
constrained grid. For comparison, the PhyloFit estimates for PhastCons regions
is much higher, at $51.23\%$. Since this would include beneficial substitutions
that would not be predicted by our model, this suggests a very high proportion
of beneficial substitutions XXX check

% This is likely due to the constrained grid placing more of the DFE mass on
% weaker selection coefficients, which in turn have a higher chance of drifting
% up to fixation.

@@

the PhastCons Priority Model is very close to CADD 6\%, and interpretable,
similiar mutation rates. This

weak selection remains elusive

UTR rates
